\paperTitle

### 2014-01-31 doc/icml2014/intro.tex

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields \todo{find a much better/broader set of citations}
\cite{quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{hsu09spectral,anandkumar11tree,anandkumar12moments,anandkumar12lda,hsu12identifiability,balle11transducer,balle12automata}.
\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, these methods apply to a limited set of models, and are thus
not as broadly applicable as EM.

>>>>

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields % \todo{find a much better/broader set of citations}
\cite{ghahramani1999variational,jaakkola2011variational,blei03lda,quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{mossel2005learning,
hsu09spectral,
bailly2010spectral,
song2011spectral,
anandkumar11tree,anandkumar12moments,anandkumar12lda,
hsu12identifiability,
balle12automata}.
%\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, these methods apply to a limited set of models, and are thus
not as broadly applicable as EM.
